Federated Learning's Blessing:\\ FedAvg has Linear Speedup

### 2020-06-03 source/sec_impact.tex
add hipaa ref

Federated learning balancing efficiency and privacy is not only an effective
tool to provide enhanced entertainment, but also a vital approach that can
save millions of lives in the short future.  Under the unprecedented outbreak
of Covid'19, coronavirus patients have filled the emergency rooms
thoroughly. It is imperative to have reliable, robust machine learning
solutions that could help doctors treat patients. However,  HIPAA regulations
impose strict restrictions on sharing patients' clinical data: privacy is a
top priority when developing machine learning techniques at those medical institutions. 
Therefore, propelling the frontiers of federated learning for more efficient 
algorithms under the privacy-preserving constraint has never been more
important.

>>>>

Federated learning balancing efficiency and privacy is not only an effective
tool to provide enhanced entertainment, but also a vital approach that can
save millions of lives in the short future.  Under the unprecedented outbreak
of Covid'19, coronavirus patients have filled the emergency rooms
thoroughly. It is imperative to have reliable, robust machine learning
solutions that could help doctors treat patients. However,  Health Insurance Portability and Accountability (HIPAA) regulations~\cite{assistance2003summary}
impose strict restrictions on sharing patients' clinical data: privacy is a
top priority when developing machine learning techniques at those medical institutions. 
Therefore, propelling the frontiers of federated learning for more efficient 
algorithms under the privacy-preserving constraint has never been more
important.
